Efficient Coalition Formation for Web Services

### 2013-04-26 papers/coalition/SCC2013_WSCoalition.tex
Changes

Web services are loosely-coupled business applications willing to
cooperate in distributed settings within different groups called
communities. Communities aim to provide better visibility,
efficiency, market share and total payoff. There are a number of
proposed mechanisms and models on aggregating web services and
making them cooperate within their communities. However, forming
optimal and stable communities as coalitions to maximize
individual and group efficiency and income has not been addressed
yet. In this paper, we propose an efficient coalition formation
mechanism using cooperative game-theoretic techniques. We propose
a mechanism for community membership requests and selections of
web services in the scenarios where established communities
already exist. Moreover, we analyze the scenarios where
communities are not established yet. The ultimate objective is to
develop a mechanism for web services to form stable groups
allowing them to maximize their efficiency and generate
near-optimal (welfare-maximizing) communities. The theoretical and
simulation results show that our algorithms provide web services
and community owners with applicable and near-optimal decision
making mechanisms.

@@

\begin{IEEEkeywords}
Web services; Cooperative game thoery; Community of services;

>>>>

Web services are loosely-coupled business applications willing to
cooperate in distributed settings within different groups called
communities. Communities aim to provide better visibility,
efficiency, market share and total payoff. There are a number of
proposed mechanisms and models on aggregating web services and
making them cooperate within their communities. However, forming
optimal and stable communities as coalitions to maximize
individual and group efficiency and income has not been addressed
yet. In this paper, we propose an efficient coalition formation
mechanism using cooperative game-theoretic techniques. We propose
a mechanism for community membership requests and selections of
web services in the scenarios where established communities
already exist. Moreover, we analyze the scenarios where
communities are not established yet and web services can form multiple communities. The ultimate objective is to
develop a mechanism for web services to form stable groups
allowing them to maximize their efficiency and generate
near-optimal (welfare-maximizing) communities. The theoretical and
simulation results show that our algorithms provide web services
and community owners with applicable and near-optimal decision
making mechanisms.

@@

\begin{IEEEkeywords}
Web services; Cooperative game theory; Community of services;
